rethinking antibiotics

### 2021-03-12 scripts/55_rethinking_abx.Rmd
ok the abx seems easier

@@

meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv') %>% 
  left_join(m)
```

>>>>

# CR/Toxicity ~ abx + center

## Toxicity

@@

meta <- read_csv('../data/amplicon/stool/combined_2_meta_expanded.csv') %>% 
  left_join(m) %>% 
  mutate(anaerobe_targeting = if_else(is.na(anaerobe_targeting), 'no', anaerobe_targeting)) %>% 
  mutate(anaerobe = if_else(anaerobe_targeting == 'no', 0, 1))

set.seed(123)
dat_list <- list(
    tox = meta$tox,
    cr100 = meta$cr100,
    location = meta$loca,
    anaerobe = meta$anaerobe
    )
```

```{r}   
atox <- ulam(
    alist(
        tox ~ dbinom( 1 , p ) ,
        logit(p) <- b*div_std + a[location] ,
        b ~ dnorm( 0 , 2), # the std of 2 is made by the later prior check
        a[location] ~ dnorm( 0 , 0.5 )
    ) , data=dat_list , chains=4 , log_lik=TRUE , cores = 8)
precis(mtox, depth = 2)
plot(precis(mtox, depth = 2) ) 
```
